Dusty galaxies and the degeneracy between their dust distributions and the attenuation formula

### 2016-03-08 paper_arxiv.tex
emulateapj version
Resize LIR vs LUV figure

\documentclass[preprint]{aastex}

%\usepackage{phoenician}

%\newcommand{\alephuv}{\textphnc{\ARaleph}$_{\mathrm{UV}}$}
%\newcommand{\alephha}{\textphnc{\ARaleph}$_{\mathrm{H}\alpha}$}
%\newcommand{\alephuvha}{\textphnc{\ARaleph}$_{0.66}$}
%\newcommand{\alephhb}{\textphnc{\ARaleph}$_{\mathrm{H}\beta}$}
\usepackage{lscape}
\usepackage{amsmath}
\newcommand{\alephuv}{f$_{\mathrm{esc}}$(0.16$\,\micron$)}
\newcommand{\alephha}{f$_{\mathrm{esc}}$(H$\alpha$)}
\newcommand{\alephuvha}{f$_{\mathrm{esc}}$(0.66$\,\micron$)}
\newcommand{\alephhb}{f$_{\mathrm{esc}}$(H$\beta$)}

@@

%This paper is organized as follows.  We present the data and derived quantities
%in \S\ref{sec:data}.  The relation is in \S\ref{sec:results}.  Our argument is
%in \S\ref{sec:discuss}.  We conclude in \S\ref{sec:conclude}.
For this paper we assume a cosmology with $H_{0} = 70$ km s$^{-1}$ Mpc $^{-1}$,
$\Omega_{\mathrm{m}} = 0.3$, and $\Omega_{\Lambda} = 0.7$.  Our terminology
is: (1) a \emph{uniform} screen is a screen equally thick between a region with
stars which ionize gas and a region with stars which emit in the UV and do not
ionize gas; (2) a \emph{dust-poor} galaxy generally has high values of UV and
H$\alpha$ escape fractions; and (3) a \emph{dusty} galaxy is selected from an IR
image and generally has low values of UV and H$\alpha$ escape fractions.  The
samples of dust-poor and dusty galaxies are not
dichotomous.  More details are in the following section.

@@

We estimate a total IR luminosity (8--1000$\,\micron$; $L_{\mathrm{IR}}$) for
each galaxy.  We redshift the \citet{chary01} template spectral energy
distributions (SEDs) to the distance of each galaxy.  If the galaxy has one
measured IR flux density, we find the SED that most closely matches that flux
density and multiply the IR luminosity of the SED by the ratio between actual
and predicted flux densities.  If the galaxy has two or more measured IR flux
densities, we introduce a multiplicative factor $f$ for each SED.  We find the
best-fit $f$ for each SED; the result is an $f$ and $\chi^{2}$ value.  We
choose the SED and its accompanying $f$ that results in the
minimum of all $\chi^{2}$ values.  The galaxy's $L_{\mathrm{IR}}$ is then $f$
times the IR luminosity of the SED.  In practice, all the high- and
low-redshift dusty galaxies have two or more measured IR flux densities, and
all the low-redshift dust-poor galaxies have one measured IR flux density.
%The uncertainty on $L_{\mathrm{IR}}$ comes from maintaining
%the signal-to-noise ratio of the flux density, in the single flux density
%case, or from $f$'s covariance matrix times its reduced $\chi^{2}$, in the
%$\chi^{2}$-fitting case.

@@

For galaxies with UV emission from newly formed massive stars the continuum
between 0.125 and 0.263$\,\micron$ is approximately a power law with index
$\beta$:
\begin{equation}
S_{\lambda} = C\lambda^{\beta}
\end{equation}
where $S_{\lambda}$ is flux density and $\lambda$ is wavelength.
We use all measured flux densities and uncertainties in this rest-frame
wavelength range to fit for $\beta$ and the constant factor $C$ or
for their limits.  Measured flux densities may be negative---the sky aperture
may be brighter than the galaxy aperture---which
complicates our fitting procedure.  When a galaxy has only two measured flux
densities in the wavelength range, the solution for $\beta$ and $C$ is
analytic, so for a solution to exist the flux densities must be positive.  If
they both are, we make no cuts on their signal-to-noise ratio (S/N).
If the only positive flux density, among multiple measurements, is $> 3\sigma$,
we calculate a $\beta$ limit using that flux density and a $3\sigma$ limit for
another in the rest-frame wavelength range.  Whether the limit is an upper or
lower one depends on whether the detected flux density's wavelength is lower
or higher than the limit's wavelength.  We do not estimate a $\beta$ limit when
the only positive flux density, among multiple measurements, is $< 3\sigma$.
If more than two measured flux densities are positive, regardless of their S/N
and whether the surplus measurements are negative or positive, we minimize
$\chi^{2}$.
%The uncertainty on $\beta$ comes from the propagation of
%flux density uncertainties, in the analytic case, or from the covariance
%matrix times the reduced $\chi^{2}$, in the $\chi^{2}$-fitting case.

@@

\begin{landscape}
\begin{deluxetable}{llllllllllllll}
\tablecolumns{14}
\tablewidth{0pc}
\tablecaption{Measured and derived quantities for the sample at $z > 0.7$
\label{tbl:highz}}
\tabletypesize{\tiny}
\tablehead{
\colhead{RA, IR} &
\colhead{Dec, IR} &
\colhead{RA, opt.} &
\colhead{Dec, opt.} &
\colhead{$z$} &
\colhead{$\beta$} &
\colhead{$\sigma_{\beta}$} &
\colhead{$0.16 \times L_{0.16}$} &
\colhead{$\sigma_{L_{0.16}}$} &
\colhead{$L_{\mathrm{H}\alpha}$} &
\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
\colhead{$L_{\mathrm{H}\alpha}$ lim.} &
\colhead{$L_{\mathrm{IR}}$} &
\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
%\colhead{UV SFR} &
%\colhead{H$\alpha$ SFR} &
%\colhead{H$\alpha$ SFR lim.} &
%\colhead{IR SFR} \\
\colhead{deg} &
\colhead{deg} &
\colhead{deg} &
\colhead{deg} &
\colhead{} &
\colhead{} &
\colhead{} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$}
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$}
}
\startdata
\cutinhead{GOODS-S}
53.113487 & -27.933195 & 53.113470 & -27.933294 & 1.098\tablenotemark{G} & 0.53 & 0.34 & 1.1e+10 & 4.9e+08 & 5.6e+08 & 2.1e+07 & \ldots & 6.2e+11 & 1.9e+10  \\
53.096371 & -27.925898 & 53.096385 & -27.925972 & 1.146 & -1.89 & 0.41 & 7.9e+09 & 3.3e+08 & 3.3e+08 & 2.6e+07 & \ldots & 2.2e+11 & 4.9e+10  \\
53.090958 & -27.922218 & 53.090977 & -27.922288 & 1.390 & 1.41 & 0.48 & 8.4e+08 & 4.5e+08 & 3.1e+08 & 2.2e+07 & \ldots & 5.5e+11 & 2.7e+10  \\
53.184750 & -27.920420 & 53.184801 & -27.920432 & 0.953 & -1.68 & 0.15 & 1.2e+10 & 3.9e+08 & 1.6e+08 & 2.3e+07 & \ldots & 9.3e+10 & 1.7e+07  \\
53.104836 & -27.913826 & 53.104830 & -27.913926 & 1.090 & 0.61 & 0.61 & 3.5e+09 & 2.7e+08 & 1.2e+08 & 1.7e+07 & \ldots & 1.8e+11 & 6.2e+09
\enddata
\tablenotetext{G}{Spectroscopic redshift solely from grism observations.}
\tablecomments{Columns: RA and Dec, IR, are positions in the
\emph{Herschel} catalogs.  They are based on positions of \emph{Spitzer}/IRAC
priors.  RA and Dec, opt., are positions in the CANDELS catalogs.
$L_{\mathrm{H}\alpha}$ lim. is a 5$\sigma$ upper limit to the H$\alpha$
line luminosity.  The entire table is published in the electronic edition of
\apj.  A portion is shown here for guidance regarding its form and content.}
\end{deluxetable}
\clearpage
\end{landscape}

\begin{landscape}
\begin{deluxetable}{llllllllllllll}
\tablecolumns{14}
\tablewidth{0pc}
\tablecaption{Measured and derived quantities for the sample at $z > 0.7$}
\tabletypesize{\tiny}
\tablehead{
\colhead{RA, IR} &
\colhead{Dec, IR} &
\colhead{RA, opt.} &
\colhead{Dec, opt.} &
\colhead{$z$} &
\colhead{$\beta$} &
\colhead{$\sigma_{\beta}$} &
\colhead{$0.16 \times L_{0.16}$} &
\colhead{$\sigma_{L_{0.16}}$} &
\colhead{$L_{\mathrm{H}\alpha}$} &
\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
\colhead{$L_{\mathrm{H}\alpha}$ lim.} &
\colhead{$L_{\mathrm{IR}}$} &
\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
%\colhead{UV SFR} &
%\colhead{H$\alpha$ SFR} &
%\colhead{H$\alpha$ SFR lim.} &
%\colhead{IR SFR} \\
\colhead{deg} &
\colhead{deg} &
\colhead{deg} &
\colhead{deg} &
\colhead{} &
\colhead{} &
\colhead{} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$}
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$}
}
\startdata
\cutinhead{GOODS-S}
53.113487 & -27.933195 & 53.113470 & -27.933294 & 1.098\tablenotemark{G} & 0.53 & 0.34 & 1.1e+10 & 4.9e+08 & 5.6e+08 & 2.1e+07 & \ldots & 6.2e+11 & 1.9e+10  \\
53.096371 & -27.925898 & 53.096385 & -27.925972 & 1.146 & -1.89 & 0.41 & 7.9e+09 & 3.3e+08 & 3.3e+08 & 2.6e+07 & \ldots & 2.2e+11 & 4.9e+10  \\
53.090958 & -27.922218 & 53.090977 & -27.922288 & 1.390 & 1.41 & 0.48 & 8.4e+08 & 4.5e+08 & 3.1e+08 & 2.2e+07 & \ldots & 5.5e+11 & 2.7e+10  \\
53.184750 & -27.920420 & 53.184801 & -27.920432 & 0.953 & -1.68 & 0.15 & 1.2e+10 & 3.9e+08 & 1.6e+08 & 2.3e+07 & \ldots & 9.3e+10 & 1.7e+07  \\
53.104836 & -27.913826 & 53.104830 & -27.913926 & 1.090 & 0.61 & 0.61 & 3.5e+09 & 2.7e+08 & 1.2e+08 & 1.7e+07 & \ldots & 1.8e+11 & 6.2e+09  \\
53.177864 & -27.909479 & 53.177902 & -27.909540 & 1.104 & -2.24 & 0.07 & 5.7e+10 & 5.9e+08 & 4.5e+08 & 1.7e+07 & \ldots & 1.1e+11 & 4.7e+09  \\
53.141853 & -27.901850 & 53.141862 & -27.901907 & 0.823 & -1.04 & 0.26 & 4.7e+09 & 3.3e+08 & 6.0e+07 & 6.7e+06 & \ldots & 9.4e+10 & 1.2e+09  \\
53.086948 & -27.901337 & 53.086917 & -27.901404 & 0.967 & -1.69 & 0.18 & 1.3e+10 & 4.4e+08 & 2.5e+08 & 1.0e+07 & \ldots & 6.1e+10 & 1.1e+08  \\
53.072140 & -27.898058 & 53.072299 & -27.898007 & 1.359 & -1.25 & 0.01 & 1.4e+10 & 1.2e+08 & 4.0e+08 & 2.0e+07 & \ldots & 2.2e+11 & 1.4e+10  \\
53.169991 & -27.895391 & 53.170031 & -27.895423 & 0.977 & -2.06 & 0.17 & 1.3e+10 & 4.5e+08 & 4.0e+08 & 1.0e+07 & \ldots & 1.7e+11 & 1.4e+10  \\
53.087067 & -27.895485 & 53.087099 & -27.895559 & 1.044 & 0.17 & 0.84 & 1.4e+09 & 1.9e+08 & \ldots & \ldots & 4.4e+07 & 1.3e+11 & 2.4e+10  \\
53.232769 & -27.891096 & 53.232826 & -27.891097 & 0.983 & -1.67 & 0.20 & 1.6e+10 & 5.7e+08 & 4.0e+08 & 3.7e+07 & \ldots & 1.9e+11 & 6.1e+09  \\
53.144283 & -27.890127 & 53.144189 & -27.890129 & 1.107 & -2.20 & 0.14 & 2.8e+10 & 5.0e+08 & 6.8e+08 & 2.9e+07 & \ldots & 4.6e+11 & 1.3e+10  \\
53.197105 & -27.890034 & 53.197131 & -27.890055 & 1.296 & 0.00 & 0.15 & 1.8e+09 & 2.1e+08 & 2.1e+08 & 2.3e+07 & \ldots & 2.0e+11 & 4.0e+08  \\
53.127056 & -27.886671 & 53.127085 & -27.886729 & 1.017 & -1.42 & 0.57 & 2.4e+09 & 2.7e+08 & 1.0e+08 & 1.3e+07 & \ldots & 8.4e+10 & 4.5e+09  \\
53.213146 & -27.885704 & 53.213217 & -27.885701 & 0.979 & -1.51 & 0.22 & 1.3e+10 & 5.3e+08 & 3.2e+08 & 5.9e+07 & \ldots & 1.4e+11 & 8.0e+09  \\
53.127460 & -27.881624 & 53.127474 & -27.881659 & 1.019 & -2.73 & 0.40 & 6.2e+09 & 4.2e+08 & 2.2e+08 & 3.1e+07 & \ldots & 1.2e+11 & 7.5e+09  \\
53.198139 & -27.878679 & 53.198186 & -27.878674 & 1.249 & -1.82 & 0.08 & 6.9e+10 & 4.7e+08 & 8.4e+08 & 4.3e+07 & \ldots & 3.6e+11 & 5.1e+10  \\
53.071480 & -27.880896 & 53.071486 & -27.880972 & 0.990 & -2.19 & 0.22 & 1.5e+10 & 5.9e+08 & \ldots & \ldots & 4.5e+08 & 1.3e+11 & 7.6e+09  \\
53.076183 & -27.873486 & 53.076058 & -27.873614 & 0.740 & -0.40 & 0.25 & 3.2e+09 & 2.5e+08 & 2.1e+08 & 9.2e+06 & \ldots & 2.0e+11 & 1.1e+10  \\
53.073376 & -27.874519 & 53.073386 & -27.874583 & 1.098 & -0.26 & 0.32 & 1.1e+10 & 4.3e+08 & 4.4e+08 & 4.6e+07 & \ldots & 3.7e+11 & 1.3e+10  \\
53.071579 & -27.872364 & 53.071535 & -27.872459 & 1.097 & 0.28 & 0.57 & 3.9e+09 & 2.8e+08 & 3.1e+08 & 2.1e+07 & \ldots & 9.6e+11 & 9.4e+10  \\
53.089268 & -27.864340 & 53.089349 & -27.864418 & 0.833 & -2.16 & 0.15 & 2.0e+10 & 7.6e+08 & 2.6e+08 & 1.1e+07 & \ldots & 6.5e+10 & 1.3e+07  \\
53.178032 & -27.866461 & 53.178037 & -27.866461 & 1.123 & -1.53 & 0.47 & 5.2e+09 & 2.9e+08 & 2.4e+08 & 1.4e+07 & \ldots & 1.8e+11 & 9.6e+08  \\
53.221905 & -27.859411 & 53.221923 & -27.859399 & 0.736 & -0.65 & 0.12 & 8.7e+09 & 3.5e+08 & \ldots & \ldots & 8.3e+07 & 8.3e+10 & 2.6e+09  \\
53.135319 & -27.861332 & 53.135431 & -27.861352 & 0.997 & -1.67 & 0.41 & 4.9e+09 & 3.5e+08 & 1.5e+08 & 7.3e+06 & \ldots & 4.6e+10 & 1.9e+08  \\
53.137783 & -27.856565 & 53.137827 & -27.856632 & 0.735 & 0.83 & 0.64 & 1.0e+09 & 2.0e+08 & \ldots & \ldots & 1.0e+08 & 5.6e+10 & 4.3e+09  \\
53.130970 & -27.860342 & 53.130982 & -27.860409 & 1.382 & -1.25 & 0.01 & 1.9e+10 & 1.3e+08 & 3.4e+08 & 2.5e+07 & \ldots & 1.4e+11 & 5.5e+07  \\
53.058479 & -27.856730 & 53.058534 & -27.856808 & 1.220 & -1.37 & 0.36 & 9.1e+09 & 2.7e+08 & \ldots & \ldots & 1.1e+08 & 1.7e+11 & 2.7e+08  \\
53.056168 & -27.855335 & 53.056169 & -27.855367 & 1.226 & -1.75 & 0.20 & 1.8e+10 & 3.1e+08 & 4.8e+08 & 3.2e+07 & \ldots & 1.5e+11 & 7.3e+09  \\
53.220245 & -27.854082 & 53.220274 & -27.854091 & 1.002 & -0.86 & 0.29 & 9.2e+09 & 4.4e+08 & 3.6e+08 & 3.7e+07 & \ldots & 4.3e+11 & 9.8e+09  \\
53.220829 & -27.851294 & 53.220908 & -27.851331 & 0.734 & 4.05 & 1.17 & 8.7e+07 & 3.4e+07 & \ldots & \ldots & 7.0e+07 & 1.4e+11 & 1.3e+10  \\
53.196545 & -27.851704 & 53.196571 & -27.851696 & 1.224 & 0.20 & 0.70 & 3.7e+09 & 2.0e+08 & 3.5e+08 & 2.3e+07 & \ldots & 6.3e+11 & 1.8e+10  \\
53.122547 & -27.852680 & 53.122554 & -27.852730 & 0.735 & 1.74 & 1.32 & 2.2e+08 & 9.1e+07 & \ldots & \ldots & 4.9e+07 & 9.6e+10 & 3.2e+09  \\
53.163998 & -27.854301 & 53.164062 & -27.854292 & 1.299\tablenotemark{G} & -0.53 & 0.09 & 2.5e+09 & 2.1e+08 & 1.4e+08 & 2.2e+07 & \ldots & 1.9e+11 & 3.7e+10  \\
53.070782 & -27.850611 & 53.070771 & -27.850671 & 0.991 & -3.56 & 0.72 & 2.8e+09 & 3.7e+08 & 1.8e+08 & 2.1e+07 & \ldots & 3.0e+11 & 8.7e+09  \\
53.104969 & -27.849974 & 53.104994 & -27.850023 & 0.841 & -2.07 & 0.14 & 1.8e+10 & 6.4e+08 & 2.0e+08 & 1.4e+07 & \ldots & 4.8e+10 & 1.5e+09  \\
53.115479 & -27.844624 & 53.115494 & -27.844666 & 1.097 & -0.94 & 0.30 & 1.1e+10 & 4.2e+08 & 6.5e+08 & 1.8e+07 & \ldots & 9.9e+11 & 8.1e+10  \\
53.214821 & -27.845755 & 53.214866 & -27.845737 & 0.980 & -2.12 & 0.68 & 3.5e+09 & 4.1e+08 & 2.1e+08 & 1.7e+07 & \ldots & 1.1e+11 & 4.7e+09  \\
53.186874 & -27.841162 & 53.186881 & -27.841169 & 0.783 & -1.43 & 0.14 & 1.2e+10 & 5.1e+08 & 1.0e+08 & 1.0e+07 & \ldots & 4.8e+10 & 2.1e+09  \\
53.055374 & -27.843821 & 53.055380 & -27.843884 & 1.296 & -0.91 & 0.10 & 4.4e+09 & 2.8e+08 & \ldots & \ldots & 1.8e+08 & 2.1e+11 & 3.2e+09  \\
53.107754 & -27.838791 & 53.107758 & -27.838812 & 1.095 & -1.93 & 0.11 & 2.7e+10 & 4.6e+08 & 1.1e+09 & 1.6e+08 & \ldots & 2.8e+11 & 6.6e+09  \\
53.109276 & -27.835032 & 53.109331 & -27.834890 & 1.096 & -1.53 & 1.40 & 1.9e+09 & 3.3e+08 & \ldots & \ldots & 1.1e+08 & 1.1e+11 & 1.3e+09  \\
53.124714 & -27.842196 & 53.124767 & -27.842230 & 1.389 & -1.04 & 0.03 & 4.1e+09 & 8.6e+07 & 1.3e+08 & 1.3e+07 & \ldots & 1.4e+11 & 6.5e+09  \\
53.214905 & -27.838238 & 53.214939 & -27.838237 & 0.853 & -1.59 & 0.09 & 3.1e+10 & 7.2e+08 & 5.1e+08 & 1.7e+07 & \ldots & 2.1e+11 & 5.8e+09  \\
53.155365 & -27.835815 & 53.155401 & -27.835815 & 1.140 & -3.21 & 0.94 & 3.9e+09 & 3.7e+08 & \ldots & \ldots & 8.0e+07 & 1.1e+11 & 1.7e+09  \\
53.215519 & -27.830894 & 53.215526 & -27.830835 & 0.736 & -0.17 & 0.15 & 7.1e+09 & 3.3e+08 & 4.6e+08 & 4.1e+07 & \ldots & 2.3e+11 & 3.3e+09  \\
53.146038 & -27.833027 & 53.146185 & -27.832905 & 1.049 & -2.17 & 0.49 & 4.9e+09 & 3.7e+08 & 1.1e+08 & 1.0e+07 & \ldots & 6.8e+10 & 1.0e+09  \\
53.218082 & -27.833673 & 53.218135 & -27.833687 & 0.853 & -1.05 & 0.21 & 8.2e+09 & 4.3e+08 & 2.6e+08 & 1.9e+07 & \ldots & 1.8e+11 & 6.5e+09  \\
53.089886 & -27.828199 & 53.089889 & -27.828241 & 1.110 & -2.10 & 0.50 & 5.7e+09 & 3.3e+08 & \ldots & \ldots & 1.1e+08 & 1.1e+11 & 1.4e+10  \\
53.216496 & -27.821653 & 53.216570 & -27.821606 & 1.247 & -1.90 & 0.34 & 1.2e+10 & 2.5e+08 & \ldots & \ldots & 1.2e+08 & 1.5e+11 & 1.8e+09  \\
53.051586 & -27.820166 & 53.051606 & -27.820193 & 1.048 & -2.14 & 0.09 & 4.2e+10 & 6.2e+08 & 1.9e+08 & 1.2e+07 & \ldots & 5.1e+10 & 4.2e+08  \\
53.074184 & -27.821064 & 53.074268 & -27.821097 & 1.127 & -2.10 & 0.17 & 1.9e+10 & 4.0e+08 & 2.3e+08 & 2.4e+07 & \ldots & 6.9e+10 & 1.7e+09  \\
53.066761 & -27.816540 & 53.066754 & -27.816593 & 1.413 & 11.31 & 11.23 & 9.3e+06 & 1.9e+09 & 3.5e+08 & 4.4e+07 & \ldots & 1.4e+12 & 6.6e+10  \\
53.181011 & -27.817177 & 53.181037 & -27.817160 & 1.370 & -0.00 & 0.31 & 2.2e+09 & 6.3e+08 & \ldots & \ldots & 2.3e+08 & 9.8e+11 & 7.5e+10  \\
53.149857 & -27.813999 & 53.149886 & -27.813998 & 1.307 & -1.44 & 0.06 & 7.6e+10 & 3.2e+09 & 8.8e+08 & 4.6e+07 & \ldots & 3.7e+11 & 3.8e+10  \\
53.044754 & -27.816416 & 53.044892 & -27.816469 & 1.380 & -0.42 & 0.16 & 3.2e+09 & 3.8e+08 & \ldots & \ldots & 1.5e+08 & 3.4e+11 & 9.3e+10  \\
53.145061 & -27.809834 & 53.145087 & -27.809851 & 1.245 & -1.87 & 0.14 & 9.4e+09 & 2.0e+08 & 2.5e+08 & 2.3e+07 & \ldots & 1.5e+11 & 2.0e+10  \\
53.164284 & -27.810833 & 53.164307 & -27.810827 & 0.735 & 0.55 & 0.28 & 5.6e+08 & 6.5e+07 & 5.9e+07 & 1.1e+07 & \ldots & 3.6e+10 & 1.6e+08  \\
53.073448 & -27.803240 & 53.073456 & -27.803292 & 0.735 & 2.17 & 1.10 & 2.3e+08 & 8.2e+07 & \ldots & \ldots & 6.6e+07 & 9.1e+10 & 1.3e+09  \\
53.066555 & -27.797188 & 53.066761 & -27.797223 & 1.296 & 1.44 & 0.14 & 1.8e+09 & 3.2e+08 & \ldots & \ldots & 1.3e+08 & 3.1e+11 & 1.4e+10  \\
53.076847 & -27.799187 & 53.076879 & -27.799206 & 1.079 & -2.19 & 0.24 & 1.3e+10 & 4.1e+08 & 1.7e+08 & 1.7e+07 & \ldots & 4.8e+10 & 7.1e+08  \\
53.034164 & -27.797775 & 53.034171 & -27.797808 & 0.840 & 0.14 & 0.21 & 4.7e+09 & 2.6e+08 & 3.1e+08 & 2.3e+07 & \ldots & 3.2e+11 & 1.1e+10  \\
53.156612 & -27.795471 & 53.156735 & -27.795577 & 1.097 & -1.51 & 0.10 & 1.5e+10 & 3.0e+08 & 2.7e+08 & 2.8e+07 & \ldots & 2.2e+11 & 2.2e+09  \\
53.022831 & -27.796343 & 53.022819 & -27.796360 & 0.898\tablenotemark{G} & -1.07 & 0.27 & 4.5e+09 & 2.9e+08 & 1.4e+08 & 9.2e+06 & \ldots & 1.1e+11 & 3.9e+09  \\
53.078960 & -27.799620 & 53.078906 & -27.799642 & 1.085 & -2.09 & 0.42 & 5.5e+09 & 3.1e+08 & 2.1e+08 & 1.1e+07 & \ldots & 6.7e+10 & 3.3e+07  \\
53.026798 & -27.791296 & 53.026811 & -27.791322 & 1.022 & -1.04 & 0.22 & 1.0e+10 & 3.7e+08 & 5.7e+08 & 1.7e+07 & \ldots & 5.2e+11 & 1.2e+10  \\
53.184113 & -27.792627 & 53.184162 & -27.792636 & 0.737 & -0.82 & 0.06 & 9.3e+09 & 2.1e+08 & 2.1e+08 & 2.6e+07 & \ldots & 1.7e+11 & 1.5e+10  \\
53.178066 & -27.792753 & 53.178077 & -27.792740 & 1.427 & -0.75 & 0.07 & 2.5e+09 & 1.1e+08 & \ldots & \ldots & 2.4e+08 & 2.8e+11 & 1.8e+08  \\
53.086002 & -27.787987 & 53.086045 & -27.788089 & 0.734 & -0.29 & 0.11 & 7.2e+09 & 2.6e+08 & \ldots & \ldots & 1.1e+08 & 1.2e+11 & 5.3e+09  \\
53.090660 & -27.790161 & 53.090665 & -27.790186 & 1.000 & -1.54 & 0.38 & 4.1e+09 & 3.0e+08 & 1.9e+08 & 1.1e+07 & \ldots & 1.1e+11 & 4.9e+09  \\
53.166122 & -27.787506 & 53.166177 & -27.787515 & 1.112 & -2.06 & 0.07 & 3.3e+10 & 4.4e+08 & 7.3e+08 & 7.6e+07 & \ldots & 3.1e+11 & 1.8e+10  \\
53.109558 & -27.788197 & 53.109568 & -27.788203 & 0.995 & -1.87 & 0.14 & 2.4e+10 & 5.8e+08 & 1.9e+08 & 1.4e+07 & \ldots & 6.0e+10 & 2.0e+08  \\
53.176544 & -27.785450 & 53.176577 & -27.785446 & 1.314 & 2.94 & 0.31 & 5.3e+08 & 1.5e+08 & 9.9e+07 & 1.7e+07 & \ldots & 3.0e+11 & 2.7e+10  \\
53.071011 & -27.785858 & 53.070981 & -27.785895 & 0.763 & -1.10 & 0.18 & 8.5e+09 & 4.5e+08 & 1.1e+08 & 1.2e+07 & \ldots & 1.2e+11 & 7.7e+08  \\
53.197544 & -27.786417 & 53.197582 & -27.786395 & 1.098 & -2.98 & 0.77 & 1.3e+09 & 2.0e+08 & \ldots & \ldots & 1.3e+08 & 2.0e+11 & 5.9e+09  \\
53.143452 & -27.783209 & 53.143470 & -27.783213 & 1.429\tablenotemark{G} & 1.30 & 1.55 & 8.1e+08 & 8.5e+08 & \ldots & \ldots & 9.3e+07 & 8.0e+11 & 2.4e+10  \\
53.104275 & -27.788363 & 53.104331 & -27.788388 & 1.357 & -0.62 & 0.20 & 4.7e+09 & 6.3e+08 & \ldots & \ldots & 8.8e+07 & 1.3e+11 & 4.9e+08  \\
53.048252 & -27.783079 & 53.048272 & -27.783100 & 0.814 & -0.53 & 0.27 & 3.8e+09 & 2.8e+08 & 1.1e+08 & 6.4e+06 & \ldots & 8.5e+10 & 1.3e+10  \\
53.135197 & -27.781746 & 53.135245 & -27.781672 & 1.437\tablenotemark{G} & -0.57 & 0.05 & 5.2e+09 & 1.9e+08 & 3.5e+08 & 1.7e+07 & \ldots & 2.5e+11 & 2.4e+10  \\
53.044064 & -27.785015 & 53.044080 & -27.785048 & 1.045 & -1.39 & 0.19 & 1.4e+10 & 4.3e+08 & 1.8e+08 & 1.4e+07 & \ldots & 2.4e+11 & 1.5e+10  \\
53.049721 & -27.779055 & 53.049747 & -27.779072 & 1.221 & -1.31 & 1.05 & 3.5e+09 & 2.5e+08 & 2.4e+08 & 2.2e+07 & \ldots & 3.1e+11 & 9.1e+09  \\
53.128693 & -27.780367 & 53.128828 & -27.780418 & 1.173 & -1.03 & 0.43 & 3.5e+09 & 2.1e+08 & 2.0e+08 & 1.4e+07 & \ldots & 2.7e+11 & 9.2e+09  \\
53.077465 & -27.780226 & 53.077453 & -27.780218 & 0.741 & 0.94 & 0.55 & 6.4e+08 & 1.1e+08 & 5.9e+07 & 7.7e+06 & \ldots & 6.2e+10 & 1.3e+09  \\
53.064384 & -27.775332 & 53.064445 & -27.775372 & 0.735 & 3.60 & 0.86 & 1.9e+08 & 5.5e+07 & \ldots & \ldots & 1.0e+08 & 2.4e+11 & 1.9e+10  \\
53.145199 & -27.777922 & 53.145238 & -27.777906 & 1.099 & -1.87 & 0.25 & 4.3e+09 & 2.0e+08 & 3.0e+08 & 1.3e+07 & \ldots & 3.0e+11 & 2.1e+10  \\
53.058456 & -27.776129 & 53.058416 & -27.776186 & 0.837 & 1.28 & 0.73 & 6.5e+08 & 1.3e+08 & 7.0e+07 & 9.0e+06 & \ldots & 2.9e+11 & 2.8e+10  \\
53.099220 & -27.777590 & 53.099269 & -27.777610 & 1.221 & -0.71 & 2.74 & 6.8e+08 & 1.4e+08 & \ldots & \ldots & 7.3e+07 & 9.6e+10 & 3.1e+08  \\

>>>>

\documentclass[iop]{emulateapj}

\usepackage{amsmath}
\newcommand{\alephuv}{f$_{\mathrm{esc}}$(0.16$\,\micron$)}
\newcommand{\alephha}{f$_{\mathrm{esc}}$(H$\alpha$)}
\newcommand{\alephuvha}{f$_{\mathrm{esc}}$(0.66$\,\micron$)}
\newcommand{\alephhb}{f$_{\mathrm{esc}}$(H$\beta$)}

@@

For this paper we assume a cosmology with $H_{0} = 70$ km s$^{-1}$ Mpc $^{-1}$,
$\Omega_{\mathrm{m}} = 0.3$, and $\Omega_{\Lambda} = 0.7$.  Our terminology
is: (1) a \emph{uniform} screen is a screen equally thick between a region with
stars which ionize gas and a region with stars which emit in the UV and do not
ionize gas; (2) a \emph{dust-poor} galaxy generally has high values of UV and
H$\alpha$ escape fractions; and (3) a \emph{dusty} galaxy is selected from an IR
image and generally has low values of UV and H$\alpha$ escape fractions.  The
samples of dust-poor and dusty galaxies are not
dichotomous.  More details are in the following section.

@@

We estimate a total IR luminosity (8--1000$\,\micron$; $L_{\mathrm{IR}}$) for
each galaxy.  We redshift the \citet{chary01} template spectral energy
distributions (SEDs) to the distance of each galaxy.  If the galaxy has one
measured IR flux density, we find the SED that most closely matches that flux
density and multiply the IR luminosity of the SED by the ratio between actual
and predicted flux densities.  If the galaxy has two or more measured IR flux
densities, we introduce a multiplicative factor $f$ for each SED.  We find the
best-fit $f$ for each SED; the result is an $f$ and $\chi^{2}$ value.  We
choose the SED and its accompanying $f$ that results in the
minimum of all $\chi^{2}$ values.  The galaxy's $L_{\mathrm{IR}}$ is then $f$
times the IR luminosity of the SED.  In practice, all the high- and
low-redshift dusty galaxies have two or more measured IR flux densities, and
all the low-redshift dust-poor galaxies have one measured IR flux density.

@@

For galaxies with UV emission from newly formed massive stars the continuum
between 0.125 and 0.263$\,\micron$ is approximately a power law with index
$\beta$:
\begin{equation}
S_{\lambda} = C\lambda^{\beta}
\end{equation}
where $S_{\lambda}$ is flux density and $\lambda$ is wavelength.
We use all measured flux densities and uncertainties in this rest-frame
wavelength range to fit for $\beta$ and the constant factor $C$ or
for their limits.  Measured flux densities may be negative---the sky aperture
may be brighter than the galaxy aperture---which
complicates our fitting procedure.  When a galaxy has only two measured flux
densities in the wavelength range, the solution for $\beta$ and $C$ is
analytic, so for a solution to exist the flux densities must be positive.  If
they both are, we make no cuts on their signal-to-noise ratio (S/N).
If the only positive flux density, among multiple measurements, is $> 3\sigma$,
we calculate a $\beta$ limit using that flux density and a $3\sigma$ limit for
another in the rest-frame wavelength range.  Whether the limit is an upper or
lower one depends on whether the detected flux density's wavelength is lower
or higher than the limit's wavelength.  We do not estimate a $\beta$ limit when
the only positive flux density, among multiple measurements, is $< 3\sigma$.
If more than two measured flux densities are positive, regardless of their S/N
and whether the surplus measurements are negative or positive, we minimize
$\chi^{2}$.

@@
